### 2016-07-27 main.tex
Begin to incorporate reviewer feedback:
- Most of the tutorial

- Reference other birds, explain why it's ok that we just show 1

- specify "Undirected song"

- LevenbUrg

- Remove fibre photometry from methods (need to remove from results; this is just an intermediate checkin so Nathan can add his bit)

We begin with a few hundred recordings of a given bird's song, in this
case made inside a sound-isolating chamber in which was mounted a
recording microphone (Audio-Technica AT803).  The songs are
time-aligned as described in \cite{Poole2012}.

@@

\noprint{
  % I screwed up: the results are without cage noise.  Rather than
  repeat all measurements, let's just not mention it.  }

With inputs well outside the space on which a neural network has been
trained, its outputs will be essentially random. In order to reduce
the false positive rate it is useful to provide negative training
examples that include silence, cage noise, non-song vocalisations, and
perhaps songs from other birds.  Although it will depend on the makeup
of the non-song data, we have found that training with as low as a 1:1
ratio of non-song to song yields excellent results.

@@

We used the Levenburg-Marquardt algorithm, which is the MATLAB
toolbox's default.  It is a fast algorithm, but is memory-intensive,
so many target syllables or high FFT frame rates require a large
amount of RAM and increase training time to hours. Other training
algorithms that use less RAM are much slower, and by default they will
often terminate prematurely due to their performance gradient going to
0.

@@

\subsection{Fibre Photometry}
\label{sec:fp-methods}

In addition to synthetic tests of detector accuracy and 
latency, we piloted the syllable detector in an experiment
providing altered auditory feedback (AAF) to zebra finches. AAF, or 
playback of a perturbing white noise stimulus, is known to disrupt 
the highly-stereotyped zebra finch song. By probabilistically 
targeting the AAF to a specific syllable, it is possible 
to selectively destabilize parts of the song. During this 
feedback, signal from genetically-encoded calcium indicators was 
recorded via fibre photometry to identify a neural representation of 
an error signals associated with the feedback.

The initial experiment design used a DSP with hand-designed filter-banks to
detect syllables, but these required tuning and were only conducive
to detecting harmonic stacks. This experiment provided an ideal design
to pilot our neural-network-based syllable detector.

\subsubsection{Surgery}

GCaMP6s and GCaMP6f were expressed using a lentivirus under the RSV 
promoter \cite{Markowitz:2015ko}. Injections were targeted under HVC 
using stimulation of Area X with a bipolar stimulation electrode. 
After injecting the virus, we implanted a fibre-optic cannula above 
HVC ($400 \mu m$ diameter, Doric Lenses). The location of the injection 
was verified histologically after each experiment.

\subsubsection{Photometry}

Fibre photometry \cite{Adelsberger:2005dy,Schulz:2012fv,Cui:2013dq,Adelsberger:2014jd,Gunaydin:2014dh} 
was performed in N=3 birds at least 2 weeks post-injection using a 
completely fibre-coupled light path. A 470 nm fibre-coupled LED (Mightex) 
was sinusoidally driven at 5 kHz by a TDT RX8. The output of the LED 
was filtered with a GFP excitation filter (Doric Lenses Fluorescence Cube) 
and coupled to an optical rotary joint (Doric Lenses). The rotary joint 
was connected via a multimode fibre optic patch cord (400 $\mu$m, .48 NA, 
Doric Lenses) to the implanted cannula using a brass sleeve (Doric Lenses). 
LED power was calibrated such that optical power at the tip was 
20--300 $\mu$W (LED was turned on only during vocalizations, detected using 
a TDT RX8). Fluorescence was collected through the same patch cord, 
filtered with a GFP emission filter, and sent to a silicon photomultiplier 
(SensL MiniSM 30000). The output of the photomultiplier was demodulated 
using a dual-phase lock-in amplifier (10-ms time-scale, SR830, Stanford 
Research Systems) and digitized along with the bird's song at 24.414 kHz 
using a National Instruments data acquisition board (PCIE-6323).

\subsubsection{Syllable detection}

User-selected syllables were detected using the Swift implementation of the
syllable detector, and the TTL output triggered altered auditory feedback 
via the TDT RX8.

\subsubsection{Data analysis}

$\Delta F / F0$ was estimated at each point by subtracting and dividing by 
F0, defined as the 11th percentile computed in a 300-ms sliding window. 
Data were then smoothed with a 50-ms exponential window. Fluorescence traces
during singing were normalized by subtracting the trial-average signal, in 
order to remove song-based modulation.

@@

@@

    \item[Runtime:]\hfill
      \begin{description}
      \item[MATLAB:] {\tt https://github.com/gardner-lab/syllable-detector-matlab}
      \item[Swift:] {\tt https://github.com/gardner-lab/syllable-detector-swift}
      \item[LabVIEW:] {\tt https://github.com/bwpearre/birds/align}
      \end{description}

>>>>

We begin with a few hundred recordings of a given bird's song.  Male
zebra finch song is most highly stereotyped when a female is present
(``directed song'') and slightly more variable otherwise
(``undirected''); we train and test on undirected song since this is
more challenging.  The songs are recorded inside a sound-isolating
chamber in which was mounted a recording microphone (Audio-Technica
AT803).  The songs are time-aligned as described in \cite{Poole2012}.

@@

With inputs well outside the space on which a neural network has been
trained, its outputs will be essentially random. In order to reduce
the false positive rate it is necessary to provide negative training
examples that include silence, cage noise, wing flapping, non-song
vocalisations, and perhaps songs from other birds.  Although it will
depend on the makeup of the non-song data, we have found that training
with as low as a 1:1 ratio of non-song to song yields excellent
results on most birds.

@@

We used the Levenberg-Marquardt algorithm, which is the MATLAB
toolbox's default.  It is a fast algorithm, but is memory-intensive,
so many target syllables or high FFT frame rates require a large
amount of RAM and increase training time to hours. Other training
algorithms that use less RAM are much slower, and by default they will
often terminate prematurely due to their performance gradient going to
0.

@@

@@

We have used this detector for song alignment and feedback experiments
in 5 behaving birds, and for offline analysis on various others.  For
simplicity we present performance on 6 randomly chosen points in one
bird's song, but the results presented here are representative of
real-world performance.\marginpar{Ok?}

@@

  \begin{description}
  \item[Installation:]\hfill
    \begin{trivlist}
    \item Clone the Github repository onto your computer.
    \end{trivlist}
  \item[Usage:]\hfill
    \begin{itemize}
      \item The main programme is {\tt learn\_detector.m}.
    \item The top section of {\tt learn\_detector.m} contains global configuration variables.  The important ones are the data directory and the bird name: as supplied, the software looks for {\tt \textless data directory\textgreater/\textless bird name\textgreater/song.mat}.  Modify as necessary.
    \item The format for the data file {\tt \textless data directory\textgreater/\textless bird name\textgreater/song.mat} is specified in {\tt birds/align/README.md}: a MATLAB file containing aligned song, nonsong (calls, cage noise, etc), and the sampling frequency.
    \item The configuration file {\tt \textless data directory\textgreater/\textless bird name\textgreater/params.m} is also described in {\tt README.md}.  If the file is empty, the programme will display an image showing the average of the song spectrograms (frequency vs.~time), tell the user how to define syllables of interest, and exit.  If {\tt times\_of\_interest} is defined, the programme will train the neural network.  {\tt params.m} can also override any of the configuration parameters at the top of {\tt learn\_detector.m}.
    \item The software will produce a neural network file, {\tt detector\_bird\_times\_\dots.mat} (the ellipses signify other information encoded in the filename).  It will also produce the audio test file described in Methods.
    \end{itemize}
  \end{description}

\item[Runtime:]\hfill
  \begin{description}
  \item[MATLAB:] {\tt https://github.com/gardner-lab/syllable-detector-matlab}
    \marginpar{Jeff: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
    \item[Usage:]\hfill
    \end{description}
  \item[Swift:] {\tt https://github.com/gardner-lab/syllable-detector-swift}
    \marginpar{Nathan: Can you flesh this out?}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item Connect the microphone through a preamp to {\em FIXME the left channel of the stereo audio input jack on the Mac Mini?}.
      \item {\em FIXME} How to connect the Arduino?  Add the Arduino programme to your GitHub?
      \item {\em FIXME} How to connect if not using Arduino?
      \end{itemize}
    \item[Usage:]\hfill
      \begin{itemize}
      \item Use {\tt convert\_to\_text.m} to convert the Matlab output file to a format easily readable by Swift.
      \item {\em FIXME} How to start Swift?  Parameters?
      \end{itemize}
    \end{description}
  \item[LabVIEW:] {\tt https://github.com/bwpearre/birds/align}
    \begin{description}
    \item[Installation:]\hfill
      \begin{trivlist}
      \item Clone the Github repository onto your computer.
      \end{trivlist}
    \item[Connection:]\hfill
      \begin{itemize}
      \item The microphone should be connected through a preamplifier to the data acquisition card, by default on Analog Input 0 (AI0).
      \item Outputs are on the Digital I/O (DIO) channels.  See the block diagram of {\tt nnfft.vi} for documentation, or just connect to DIO0.
      \end{itemize}
    \item[Usage:]\hfill
      Use LabVIEW to open {\tt nnfft.vi}.  A file
      chooser is provided in the front panel.  Use it to point to the network file
      produced by {\tt learn\_detector.m}, and use LabView's ``Run''
      button to begin detection.
    \end{description}
  \end{description}
